---
output: github_document
---

# mlr3filters

[![Travis build
status](https://travis-ci.org/mlr-org/mlr3filters.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3filters)
[![CRAN
status](https://www.r-pkg.org/badges/version/mlr3filters)](https://cran.r-project.org/package=mlr3filters)
[![Coverage
status](https://codecov.io/gh/mlr-org/mlr3filters/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3filters?branch=master)
[![StackOverflow](https://img.shields.io/badge/stackoverflow-mlr3-orange.svg)](https://stackoverflow.com/questions/tagged/mlr3)

_mlr3filters_ adds filters, feature selection methods and embedded feature selection methods of algorithms to _mlr3_.


## Installation

```{r eval = FALSE}
remotes::install_github("mlr-org/mlr3filters")
```

## Filters

### Filter Example

```{r}
library("mlr3")
library("mlr3filters")

task = mlr_tasks$get("pima")
filter = mlr_filters$get("auc")
as.data.table(filter$calculate(task))
```

### Implemented Filters

```{r echo = FALSE, message=FALSE}
library("mlr3filters")
library("data.table")

capitalize <- function(x) {
  substr(x, 1, 1) <- toupper(substr(x, 1, 1))
  x
}

link_cran = function(x) {
  ifelse(x %in% getOption("defaultPackages"), x, sprintf("[%1$s](https://cran.r-project.org/package=%1$s)", x))
}

tab = as.data.table(mlr_filters)[, !c("param_set", "task_properties")]
tab[, task_type := sapply(task_type, function(x) paste(capitalize(x), collapse = " & "))]
tab[, feature_types := sapply(feature_types, function(x) paste(capitalize(x), collapse = ", "))]
tab[, packages := link_cran(packages)]
setnames(tab,
  old = c("key", "task_type", "feature_types", "packages"),
  new = c("Name", "Task Type", "Feature Types", "Package"))
knitr::kable(tab[order(Name)], escape = F, format = "markdown")
```

### Variable Importance Filters

The following learners allow the extraction of variable importance and therefore are supported by `FilterImportance`:

```{r echo=FALSE}
library("mlr3learners")
tab = as.data.table(mlr_learners)
tab[sapply(properties, is.element, el = "importance"), key]
```

If your learner is listed here, the reason is most likely that it is not integrated into [mlr3learners](https://github.com/mlr-org/mlr3learners) or [mlr3extralearners](https://github.com/mlr-org/mlr3extralearners).
Please open an issue so we can add your package.

Some learners need to have their variable importance measure "activated" during learner creation.
For example, to use the "impurity" measure of Random Forest via the _ranger_ package:

```{r }
task = mlr_tasks$get("iris")
lrn = mlr_learners$get("classif.ranger",
  param_vals = list(importance = "impurity"))

filter = FilterImportance$new(learner = lrn)
filter$calculate(task)
head(as.data.table(filter), 3)
```

### Performance Filter

`FilterPerformance` is a univariate filter method which calls `resample()` with every predictor variable in the dataset and ranks the final outcome using the supplied measure.
Any learner can be passed to this filter with `classif.rpart` being the default.
