---
output: github_document
---

# mlr3filters

Package website: [release](https://mlr3filters.mlr-org.com/) | [dev](https://mlr3filters.mlr-org.com/dev)

{mlr3filters} adds filters, feature selection methods and embedded feature selection methods of algorithms to {mlr3}.

<!-- badges: start -->
[![R CMD Check via {tic}](https://img.shields.io/github/workflow/status/mlr-org/mlr3filters/R%20CMD%20Check%20via%20%7Btic%7D?logo=github&label=R CMD Check via {tic}&style=flat-square)](https://github.com/mlr-org/mlr3filters/actions)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3filters)](https://cran.r-project.org/package=mlr3filters)
[![CRAN checks](https://cranchecks.info/badges/worst/mlr3filters)](https://cran.r-project.org/web/checks/check_results_mlr3filters.html)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3filters/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3filters?branch=master)
[![StackOverflow](https://img.shields.io/badge/stackoverflow-mlr3-orange.svg)](https://stackoverflow.com/questions/tagged/mlr3)
<!-- badges: end -->

## Installation

CRAN version

```{r eval = FALSE}
install.packages("mlr3filters")
```

Development version

```{r, eval = FALSE}
remotes::install_github("mlr-org/mlr3filters")
```

## Filters

### Filter Example

```{r}
set.seed(1)
library("mlr3")
library("mlr3filters")

task = tsk("pima")
filter = flt("auc")
as.data.table(filter$calculate(task))
```

### Implemented Filters

```{r echo = FALSE, message=FALSE}
library("mlr3filters")
library("data.table")

capitalize <- function(x) {
  substr(x, 1, 1) <- toupper(substr(x, 1, 1))
  x
}

link_cran = function(x) {
  ifelse(x %in% getOption("defaultPackages"), x, sprintf("[%1$s](https://cran.r-project.org/package=%1$s)", x))
}

tab = as.data.table(mlr_filters)[, !c("param_set", "task_properties")]
tab[, task_type := sapply(task_type, function(x) paste(capitalize(x), collapse = " & "))]
tab[, feature_types := sapply(feature_types, function(x) paste(capitalize(x), collapse = ", "))]
tab[, packages := link_cran(packages)]
setnames(tab,
  old = c("key", "task_type", "feature_types", "packages"),
  new = c("Name", "Task Type", "Feature Types", "Package"))
# manually change the task type for filter "performance"
tab[Name == "performance", `Task Type` := "Universal"]
tab[Name == "importance", `Task Type` := "Universal"]
knitr::kable(tab[order(Name)], escape = F, format = "markdown")
```

### Variable Importance Filters

The following learners allow the extraction of variable importance and therefore are supported by `FilterImportance`:

```{r echo=FALSE, warning=FALSE}
library("mlr3learners")
tab = as.data.table(mlr_learners)
tab[sapply(properties, is.element, el = "importance"), key]
```

If your learner is not listed here but capable of extracting variable importance from the fitted model, the reason is most likely that it is not yet integrated in the package [mlr3learners](https://github.com/mlr-org/mlr3learners) or the [extra learner organization](https://github.com/mlr3learners).
Please open an issue so we can add your package.

Some learners need to have their variable importance measure "activated" during learner creation.
For example, to use the "impurity" measure of Random Forest via the {ranger} package:

```{r }
task = tsk("iris")
lrn = lrn("classif.ranger")
lrn$param_set$values = list(importance = "impurity")

filter = flt("importance", learner = lrn)
filter$calculate(task)
head(as.data.table(filter), 3)
```

### Performance Filter

`FilterPerformance` is a univariate filter method which calls `resample()` with every predictor variable in the dataset and ranks the final outcome using the supplied measure.
Any learner can be passed to this filter with `classif.rpart` being the default.
Of course, also regression learners can be passed if the task is of type "regr".
